---
title: "Fake News Project Book"
author: "Svyatoslav Andriyishen, Hanah Chang, Bob Chen, Stephanie Park"
date: "March 23, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Packages, echo = FALSE, results = 'hide', message = FALSE, warning = FALSE}
if (!require("dplyr")) {
 install.packages("dplyr", dependencies = TRUE)
  library(dplyr)}
if (!require("tidyr")) {
 install.packages("tidyr", dependencies = TRUE)
  library(tidyr)}
if (!require("ggplot2")) {
 install.packages("ggplot2", dependencies = TRUE)
  library(ggplot2)}
if (!require("ggthemes")) {
 install.packages("ggthemes", dependencies = TRUE)
  library(ggthemes)}
if (!require("tidytext")) {
 install.packages("tidytext", dependencies = TRUE)
  library(tidytext)}
if (!require("quanteda")) {
 install.packages("quanteda", dependencies = TRUE)
  library(quanteda)}
if (!require("tm")) {
 install.packages("tm", dependencies = TRUE)
  library(tm)}
if (!require("stringr")) {
 install.packages("stringr", dependencies = TRUE)
  library(stringr)}
if (!require("qdap")) {
 install.packages("qdap", dependencies = TRUE)
  library(qdap)}
if (!require("qdapDictionaries")) {
 install.packages("qdapDictionaries", dependencies = TRUE)
  library(qdapDictionaries)}
if (!require("plotly")) {
 install.packages("plotly", dependencies = TRUE)
  library(plotly)}
if (!require("scales")) {
 install.packages("scales", dependencies = TRUE)
  library(scales)}
if (!require("DT")) {
 install.packages("DT", dependencies = TRUE)
  library(DT)}
if (!require("leaflet")) {
 install.packages("leaflet", dependencies = TRUE)
  library(leaflet)}
if (!require("rgdal")) {
 install.packages("rgdal", dependencies = TRUE)
  library(rgdal)}
if (!require("tigris")) {
 install.packages("tigris", dependencies = TRUE)
  library(tigris)}
if (!require("sp")) {
 install.packages("sp", dependencies = TRUE)
  library(sp)}
if (!require("plyr")) {
 install.packages("plyr", dependencies = TRUE)
  library(plyr)}
```


## Intro

On its March 2017 issue, Time Magazine's headline read "Is Truth Dead?" As information is becoming increasingly accessible, the question of what information we should trust is becoming similarly as relevant. Trust and confidence in the media is dropping throughout the world.

## WVS

```{r WVS, echo = FALSE, results = 'hide', message = FALSE, warning = FALSE}
# Import and format data
load("WV6_Data_R_v_2016_01_01.rdata")

list_r <- c("8##Albania
12##Algeria
16##American Samoa
20##Andorra
24##Angola
28##Antigua
31##Azerbaijan
32##Argentina
36##Australia
40##Austria
48##Bahrain
50##Bangladesh
51##Armenia
52##Barbados
56##Belgium
60##Bermuda
64##Bhutan
68##Bolivia
70##Bosnia
72##Botswana
76##Brazil
84##Belize
100##Bulgaria
104##Myanmar
108##Burundi
112##Belarus
116##Cambodia
120##Cameroon
124##Canada
144##Sri Lanka
148##Chad
152##Chile
156##China
158##Taiwan
170##Colombia
180##D.R. Congo
184##Cook Islands
188##Costa Rica
191##Croatia
192##Cuba
196##Cyprus (G)
197##Cyprus (T)
203##Czech Rep.
208##Denmark
214##Dominican Rep.
218##Ecuador
222##El Salvador
226##Eq.Guinea
231##Ethiopia
232##Eritrea
233##Estonia
246##Finland
250##France
268##Georgia
270##Gambia
275##Palestine
276##Germany
288##Ghana
292##Gibraltar
300##Greece
320##Guatemala
324##Guinea
328##Guyana
332##Haiti
340##Honduras
344##Hong Kong
348##Hungary
352##Iceland
356##India
360##Indonesia
364##Iran
368##Iraq
372##Ireland
376##Israel
380##Italy
384##Côte dIvoire
388##Jamaica
392##Japan
398##Kazakhstan
400##Jordan
404##Kenya
408##North Korea
410##South Korea
414##Kuwait
417##Kyrgyzstan
418##Laos
422##Lebanon
426##Lesotho
428##Latvia
430##Liberia
434##Libya
438##Liechtenstein
440##Lithuania
442##Luxembourg
450##Madagascar
454##Malawi
458##Malaysia
466##Mali
470##Malta
474##Martinique
478##Mauritania
480##Mauritius
484##Mexico
492##Monaco
496##Mongolia
498##Moldova
504##Morocco
508##Mozambique
512##Oman
516##Namibia
524##Nepal
528##Netherlands
554##New Zealand
558##Nicaragua
562##Niger
566##Nigeria
578##Norway
586##Pakistan
591##Panama
598##Papua New Guinea
600##Paraguay
604##Peru
608##Philippines
616##Poland
620##Portugal
624##Guinea-Bissau
626##Timor-Leste
630##Puerto Rico
634##Qatar
642##Romania
643##Russia
646##Rwanda
682##Saudi Arabia
686##Senegal
690##Seychelles
694##Sierra Leone
702##Singapore
703##Slovakia
704##Viet Nam
705##Slovenia
706##Somalia
710##South Africa
716##Zimbabwe
724##Spain
736##Sudan
740##Suriname
752##Sweden
756##Switzerland
760##Syria
762##Tajikistan
764##Thailand
768##Togo
780##Trinidad and Tobago
784##United Arab Emirates
788##Tunisia
792##Turkey
795##Turkmenistan
800##Uganda
804##Ukraine
807##Macedonia
818##Egypt
826##Great Britain
834##Tanzania
840##United States
850##U.S. Virgin Islands
854##Burkina Faso
858##Uruguay
860##Uzbekistan
862##Venezuela
887##Yemen
891##Serbia and Montenegro
894##Zambia
900##West Germany
901##East Germany
902##Tambov
903##Moscow
904##Basque Country
906##Andalusia
907##Galicia
909##North Ireland
910##Valencia
911##Serbia
912##Montenegro
913##Srpska Republic
914##Bosnian Federation
915##Kosovo
")

list <- gsub( "##", ",", list_r)
list <- gsub( "\n", ";", list)
list <- as.data.frame(list)
list <- unlist(strsplit(as.character(list$list),split = ";"))
list <- as.data.frame(list)
list$V2 <- list$list
list <- str_split(list$V2, ",")
list <- as.data.frame(list)
list <- t(list)
list <- as.data.frame(list)
list$Country <- list$V2
list$V2 <- list$V1
WV6 <- merge(WV6_Data_R, list, by.x="V2", by.y="V2")
WV6$Year <- WV6$V262
WV6$Conf <- WV6$V110

# Subset and compute means
WV6 <- subset(WV6, WV6$Conf > 0)
mean_w <- aggregate(Conf ~ Year, data = WV6, FUN = function (x) mean(x))
mean_d <- aggregate(Conf ~ Country + Year, data = WV6, FUN = function(x) mean(x))

# Explanatory: Plot average press confindence
# p1 <- ggplot(data = mean_w, aes(x = Conf, y = Year, col = Year)) + geom_point() + labs(title = "Confidence in Press - World Average", x = "         ") + scale_y_continuous(trans = "reverse")
# p1 <- p1 + scale_x_continuous(limits = c(1, 4), breaks = c(1, 2, 3, 4), label = c("1<br>A great deal", "2<br>Quite a lot", "3<br>Not very much", "4<br>None at all"))
# p1 <- ggplotly(p1)
# p1 

# p2 <- ggplot(data = mean_d, aes(x = Conf, y = Year, col = Country)) + geom_point() + labs(title = "Confidence in Press", x =  "         ") + scale_y_continuous(trans = "reverse")
# p2 <- p2 + scale_x_continuous(limits = c(1, 4), breaks = c(1, 2, 3, 4), label = c("1<br>A great deal", "2<br>Quite a lot", "3<br>Not very much", "4<br>None at all"))
# p2 <- ggplotly(p2)
# p2 

# Subset and recode for educational levels
WV6 <- subset(WV6, WV6$V248 > 0 &  WV6$V248 < 10 )
WV6$Year <- WV6$V262
WV6$Conf <- WV6$V110
WV6$Region <- WV6$V256
WV6$Edu <- WV6$V248
WV6$Edu[WV6$V248 == 1] <- "No formal education"
WV6$Edu[WV6$V248 == 2] <- "Incomplete primary school"
WV6$Edu[WV6$V248 == 3] <- "Complete primary school"
WV6$Edu[WV6$V248 == 4] <- "Incomplete secondary school"
WV6$Edu[WV6$V248 == 5] <- "Complete secondary school"
WV6$Edu[WV6$V248 == 6] <- "Incomplete secondary school"
WV6$Edu[WV6$V248 == 7] <- "Complete secondary school"
WV6$Edu[WV6$V248 == 8] <- "Some university-level education"
WV6$Edu[WV6$V248 == 9] <- "University - level education"
WV6$Edu <- as.factor(WV6$Edu)
WV6$EduLevel <- WV6$V248

WV6$Conf_text <- WV6$Conf
WV6$Conf_text[WV6$Conf == 1] <- "A great deal"
WV6$Conf_text[WV6$Conf == 2] <- "Quite a lot"
WV6$Conf_text[WV6$Conf == 3] <- "Not very much"
WV6$Conf_text[WV6$Conf == 4] <- "None at all"
WV6$Conf_text <- as.factor(WV6$Conf_text)

mean_conf <- aggregate(Conf ~ Country, data = WV6, FUN = function(x) mean(x))
mean_edu <- aggregate(EduLevel ~ Country, data = WV6, FUN = function(x) mean(x))

edu1 <- WV6 %>%
   group_by(Country) %>%
   summarize(No.Edu = mean(V248 == 1))
edu2 <- WV6 %>%
   group_by(Country) %>%
   summarize(Primary = mean(V248 == 2 | V248 == 3))
edu3 <- WV6 %>%
   group_by(Country) %>%
   summarize(Secondary = mean(V248 == 4 | V248 == 5 |V248 == 6|V248 == 7))
edu4 <- WV6 %>%
   group_by(Country) %>%
   summarize(University = mean(V248 == 8 | V248 == 9))
edu1$Country <- rownames(edu1)
edu2$Country <- rownames(edu2)
edu3$Country <- rownames(edu3)
edu4$Country <- rownames(edu4)
Countrynames <- unique(WV6$Country)
Countrynames <- data.frame(Countrynames)
Countrynames$Country <-rownames(Countrynames)
# Countrynames

Edu <- join_all(list(edu1, edu2, edu3, edu4, Countrynames), by = 'Country', type = 'full')
Edu$Country <- Edu$Countrynames

mean_dt <- join(mean_conf, mean_edu,
     type = "inner")
mean_dt <- join(mean_dt, Edu, type = 'full')
percent <- function(x, digits = 2, format = "f", ...) 
  {
  paste0(formatC(100 * x, format = format, digits = digits, ...), "%")
}
mean_dt$No.Edu <- percent(mean_dt$No.Edu)
mean_dt$Primary <- percent(mean_dt$Primary)
mean_dt$Secondary <- percent(mean_dt$Secondary)
mean_dt$University <- percent(mean_dt$University)

# Explanatory data table
# WV6_dt <- datatable(mean_dt[c("Country","EduLevel","Conf","No.Edu","Primary","Secondary","University")])
# WV6_dt

# Get data for Leaflet
download.file(file.path('http://www.naturalearthdata.com/http/',
                        'www.naturalearthdata.com/download/50m/cultural',
                        'ne_50m_admin_0_countries.zip'), 
              f <- tempfile())
unzip(f, exdir=tempdir())
world <- readOGR(tempdir(), 'ne_50m_admin_0_countries', encoding='UTF-8')

world_dat <- merge(world, mean_dt, by.x="name_long", by.y="Country")

# Plot leaflet
m = leaflet(world_dat) %>% 
    setView(lat=10, lng=0 , zoom=2) %>% 
    addTiles(group = "OpenStreetMap") %>%
    addProviderTiles(providers$Stamen.Toner, group = "Toner")  %>%
    addProviderTiles(providers$Stamen.TonerLite, group = "Toner Lite") %>%
  
    addPolygons(group="Confidence Level",
    stroke = FALSE, fillOpacity = 0.5, smoothFactor = 0.5, 
    color = ~colorQuantile("RdYlGn", Conf)(Conf),
    popup = paste("Country:",world_dat$name_long,"<br/>",
                  "Confidence in Press:", round(world_dat$Conf,1),"<br/>",
                  "Average Education Level:",round(world_dat$EduLevel,0)))
m <- m %>%
     addPolygons(group="% by Edu Level",
     stroke = FALSE, color = ~colorQuantile("RdYlGn", EduLevel)(EduLevel), 
     popup = paste("No Education:",world_dat$No.Edu,"<br/>","Primary:",world_dat$Primary,"<br/>","Secondary:",world_dat$Secondary,"<br/>","University:",world_dat$University))
m <- m %>%
    addLayersControl(
    baseGroups = c("OpenStreetMap", "Toner", "Toner Lite"),
    overlayGroups = c("Confidence Level","% by Edu Level"),
    options = layersControlOptions(collapsed = TRUE))
m <- m %>% addLegend("bottomright", 
    pal = colorNumeric("RdYlGn", world_dat$conf), values = ~Conf,
    title = "Confidence in Press <br> 1 = A great deal<br>2 = Quite a lot<br>3 = Not very much<br>4 = None at all", opacity = 0.5)
```

```{r, echo = FALSE}
# plot leaflet in another chunk for optimized visualization
m
```

## GSS 72-16

For defining what states comprise the various values of the `region` variable in the GSS (actual states are masked for respondents for privacy concerns), the following U.S. Census map of regions of the United States was used:
https://www2.census.gov/geo/pdfs/maps-data/maps/reference/us_regdiv.pdf

```{r GSS2, echo = FALSE, results = 'hide', message = FALSE, warning = FALSE}
detach("package:plyr", unload=TRUE)
# Import data
load("gss_sub.rda")
gss_sub$conpress <- 3 - gss_sub$conpress
gss_sub$trust <- 3 - gss_sub$trust
gss_sub$contv <- 3 - gss_sub$contv
gss_sub$confinan <- 3 - gss_sub$confinan
gss_sub$conbus <- 3 - gss_sub$conbus
gss_sub$conclerg <- 3 - gss_sub$conclerg
gss_sub$coneduc <- 3 - gss_sub$coneduc
gss_sub$confed <- 3 - gss_sub$confed
gss_sub$conmedic <- 3 - gss_sub$conmedic
gss_sub$conjudge <- 3 - gss_sub$conjudge
gss_sub$consci <- 3 - gss_sub$consci
gss_sub$conlegis <- 3 - gss_sub$conlegis
gss_sub$conarmy <- 3 - gss_sub$conarmy
gss_sub$conlabor <- 3 - gss_sub$conlabor

#filter out 2016
gss_16 <- filter(gss_sub, year == 2016)

gss_ly <- gss_sub %>% group_by(year) %>%
  summarize(General = mean(trust, na.rm = TRUE),
            Press = mean(conpress, na.rm = TRUE), 
            TV = mean(contv, na.rm = TRUE),
            Finance = mean(confinan, na.rm = TRUE),
            Business = mean(conbus, na.rm = TRUE),
            Religion = mean(conclerg, na.rm = TRUE),
            Education = mean(coneduc, na.rm = TRUE),
            Exec_fed_gov = mean(confed, na.rm = TRUE),
            Unions = mean(conlabor, na.rm = TRUE),
            Medicine = mean(conmedic, na.rm = TRUE),
            Supreme_court = mean(conjudge, na.rm = TRUE),
            Science_comm = mean(consci, na.rm = TRUE),
            Congress = mean(conlegis, na.rm = TRUE),
            Military = mean(conarmy, na.rm = TRUE))

if (!require("plotly")) {
 install.packages("plotly", dependencies = TRUE)
  library(plotly)}
if (!require("RColorBrewer")) {
 install.packages("RColorBrewer", dependencies = TRUE)
  library(RColorBrewer)}


plot_ly(gss_ly, x = ~year, y = ~General, type = "scatter", mode = "lines+markers", 
        connectgaps = TRUE, name = "General Trust Level") %>%
  add_trace(y = ~Press, name = "Press") %>%
  add_trace(y = ~TV, name = "TV") %>%
  add_trace(y = ~Finance, name = "Finance") %>%
  add_trace(y = ~Business, name = "Business") %>%
  add_trace(y = ~Religion, name = "Religion") %>%
  add_trace(y = ~Education, name = "Education") %>%
  add_trace(y = ~Medicine, name = "Medicine") %>%
  add_trace(y = ~Science_comm, name = "Scientific Community") %>%
  add_trace(y = ~Unions, name = "Organized Labor") %>%
  add_trace(y = ~Exec_fed_gov, name = "Executive Federal Government") %>%
  add_trace(y = ~Supreme_court, name = "Supreme Court") %>%
  add_trace(y = ~Congress, name = "Congress") %>%
  add_trace(y = ~Military, name = "Military") %>%
  layout(title = "Yearly Trends in GSS Confidence Variables",
         yaxis = list(title = "Confidence Level"),
         xaxis = list(title = "Year"))

US_map <- tigris::divisions()

# GSS summary by region
gss_by_reg <- gss_16 %>% group_by(region) %>%
  summarize(General = mean(trust, na.rm = TRUE),
            Press = mean(conpress, na.rm = TRUE), 
            TV = mean(contv, na.rm = TRUE),
            Finance = mean(confinan, na.rm = TRUE),
            Business = mean(conbus, na.rm = TRUE),
            Religion = mean(conclerg, na.rm = TRUE),
            Education = mean(coneduc, na.rm = TRUE),
            Exec_fed_gov = mean(confed, na.rm = TRUE),
            Unions = mean(conlabor, na.rm = TRUE),
            Medicine = mean(conmedic, na.rm = TRUE),
            Supreme_court = mean(conjudge, na.rm = TRUE),
            Science_comm = mean(consci, na.rm = TRUE),
            Congress = mean(conlegis, na.rm = TRUE),
            Military = mean(conarmy, na.rm = TRUE))
gss_by_reg <- data.frame(sapply(gss_by_reg, function(x) as.numeric(as.character(x))))
gss_by_reg$region <- as.character(gss_by_reg$region)

US_map@data <- US_map@data %>%
  left_join(gss_by_reg, by = c("DIVISIONCE" = "region"))

if (!require("leaflet")) {
 install.packages("leaflet", dependencies = TRUE)
  library(leaflet)}

# US Regional Map of Confidence in Press
leaflet(US_map) %>% addTiles() %>%
  setView(lat=38.0000, lng=-97.0000, zoom = 4) %>%
  addPolygons(fillColor = topo.colors(17, alpha = NULL), stroke = FALSE,
              fillOpacity = 0.5, smoothFactor = 0.5, 
              color = ~colorQuantile("RdYlGn", Press)(Press),
              popup = paste("Region:", US_map$NAME,"<br/>",
                  "Confidence in Press:", round(as.numeric(US_map$Press), 2),"<br/>",
                  "Confidence in TV:", round(as.numeric(US_map$TV), 2)))

# simple regressions to check for correlations

# regress over entire GSS dataset
summary(lm(conpress ~ ., data = gss_sub))


# pick variables for 2016-only regression because of NA issues
# some variables had all NA for each response to conpress, so the entire data was omitted
# and we had to hand pick variables
# also removed contv due to covariance with conpress
summary(lm(conpress ~ trust + confinan + coneduc + conlabor +
             conmedic + conjudge + consci + conlegis + conarmy +
             partyid + born + age + marital + adults + degree + race +
             relig, data = gss_16))

partynames <- c("Strong Democrat", "Not Strong Democrat", "Independent near Democrat", 
                        "Independent", "Independent near Republican", "Not Strong Republican", 
                        "Strong Republican", "Other")
gss_16$partyid <- as.factor(gss_16$partyid)
levels(gss_16$partyid) <- partynames
gss_16 <- within(gss_16, partyid <- relevel(partyid, ref = "Other"))
summary(lm(conpress ~ partyid, data = gss_16))

# Confidence in Press level by Political Affiliation in 2016
ggplot(gss_16[!is.na(gss_16$partyid),], aes(x = as.factor(partyid), fill = as.factor(partyid))) +
  stat_summary(aes(y = as.numeric(conpress)), fun.y = "mean", geom = "bar") + 
  coord_flip() + theme(legend.position = "none", axis.text.x = element_text(angle=90)) +
  scale_y_continuous(limits = c(0, 2), breaks = 0:2, labels = c("Hardly any", "Only some", "A great deal")) +
  labs(title = "Confidence in Press Levels by Political Affiliation",
       y = "Confidence in the Press", x = "")
```

```{r GSS, echo = FALSE, results = 'hide', message = FALSE, warning = FALSE}
# Import data
gss_sub2 <- read.csv("gss_sub.csv")
gss_sub2$conpress <- 3 - gss_sub2$conpress
yr16 <- subset(gss_sub2, gss_sub2$year == 2016)

# Confidence in Media by age group

age16 <- na.omit(yr16[,c("age_group","conpress")])

byage <- age16 %>%
  group_by(age_group)%>%
  summarize(mean_scores = mean(conpress))%>%
  ggplot(aes(x = age_group, y = mean_scores, fill = age_group,alpha=0.3)) +
  geom_bar(stat = "identity") + geom_text(aes(label=round(mean_scores,2), size = 10, fontface = "bold", vjust=4))+ labs(x = "Age Group", y = "Confidence Level")+ggtitle("Confidence in Media by Age Group") + theme(plot.title=element_text(size=rel(1.1), lineheight=.9,face="italic",colour="black"))+ theme_tufte()+theme(legend.position="none")+ scale_y_continuous(limit = c(0,2), breaks = c(0,1,2), labels = c("Hardly Any", "Only some", "A great deal"))

byage

# Confidence in Media by race

race16 <- na.omit(yr16[,c("race","conpress")])

byrace <- race16 %>%
  group_by(race)%>%
  summarize(mean_scores = mean(conpress))%>%
  ggplot(aes(x = race, y = mean_scores, fill = race,alpha=0.3)) + geom_bar(stat = "identity") + geom_text(aes(label=round(mean_scores,2), size = 10, fontface = "bold", vjust=4))+ labs(x = "Race", y = "Confidence Level")+ggtitle("Confidence in Media by Race") + theme(plot.title=element_text(size=rel(1.1), lineheight=.9,face="italic",colour="black"))+ theme_tufte()+theme(legend.position="none")+ scale_y_continuous(limit = c(0,2), breaks = c(0,1,2), labels = c("Hardly Any", "Only some", "A great deal"))+ scale_x_discrete(limit = c("1", "2", "3"), labels = c("White","Black","Other"))

byrace

# Confidence in Media by born

born16 <- na.omit(yr16[,c("born","conpress")])

byborn <- born16 %>%
  group_by(born)%>%
  summarize(mean_scores = mean(conpress))%>%
  ggplot(aes(x = born, y = mean_scores, fill = born,alpha=0.3)) + geom_bar(stat = "identity") + geom_text(aes(label=round(mean_scores,2), size = 10, fontface = "bold", vjust=4))+ labs(x = "Birthplace", y = "Confidence Level")+ggtitle("Confidence in Media by Birthplace") + theme(plot.title=element_text(size=rel(1.1), lineheight=.9,face="italic",colour="black"))+ theme_tufte()+theme(legend.position="none")+ scale_x_discrete(limit = c("1", "2"), labels = c("Born in the U.S","Not Born in the U.S.")) + scale_y_continuous(limit = c(0,2), breaks = c(0,1,2), labels = c("Hardly Any", "Only some", "A great deal"))

byborn
```

# New York Times

```{r NYT, echo = FALSE, results = 'hide', message = FALSE, warning = FALSE}
# Import and clean subjects
library(dplyr)
library(stringr)

nyt2016 <- read.csv("/Users/bobchen/Documents/Columbia/S17/4063 Data Visualization/final-project-team-8/Data/nyt2016.csv")

sub2016 <- select(nyt2016, SUBJECT)
sub2016 <- gsub( " *\\(.*?\\) *", "", sub2016$SUBJECT) # Remove parentheses
sub2016 <- strsplit(sub2016, ";") # Split by ';' into a list
sub2016 <- lapply(sub2016, FUN = trimws) # Remove whitespace
sub2016list <- unique(unlist(sub2016))

nyt2012 <- read.csv("/Users/bobchen/Documents/Columbia/S17/4063 Data Visualization/final-project-team-8/Data/nyt2012.csv")

sub2012 <- select(nyt2012, SUBJECT)
sub2012 <- gsub( " *\\(.*?\\) *", "", sub2012$SUBJECT) # Remove parentheses
sub2012 <- strsplit(sub2012, ";") # Split by ';' into a list
sub2012 <- lapply(sub2012, FUN = trimws) # Remove whitespace
sub2012list <- unique(unlist(sub2012))

nyt2008 <- read.csv("/Users/bobchen/Documents/Columbia/S17/4063 Data Visualization/final-project-team-8/Data/nyt2008.csv")

sub2008 <- select(nyt2008, SUBJECT)
sub2008 <- gsub( " *\\(.*?\\) *", "", sub2008$SUBJECT) # Remove parentheses
sub2008 <- strsplit(sub2008, ";") # Split by ';' into a list
sub2008 <- lapply(sub2008, FUN = trimws) # Remove whitespace
sub2008list <- unique(unlist(sub2008))

s16 <- paste(sub2016list, collapse = " ")
s12 <- paste(sub2012list, collapse = " ")
s08 <- paste(sub2008list, collapse = " ")

# Combine and convert data for plotting
all <- c(s16, s12, s08)
corpus2 <- Corpus(VectorSource(all)) # create corpus
cloudtdm <- TermDocumentMatrix(corpus2) # create term document matrix
cloudtdm <- as.matrix(cloudtdm) # convert as matrix
colnames(cloudtdm) <- c("2016", "2012", "2008") # add column names

# Plot the word cloud
library(wordcloud)
set.seed(999)

comparison.cloud(cloudtdm, random.order=FALSE,
colors = brewer.pal(3, "Set1"),
title.size = 1.5, max.words = 200)
```


## NPS 2008

```{r NPS, echo = FALSE, message = FALSE, warning = FALSE}
# Import data
data2 <- read.csv("nps2008.csv", header=T, na.strings=c("","NA"))
data3 <- data2[, c("R_STATE", "QB2_A","QB2_B","QB2_C","QB2_D")] # group by states 
data3 <- na.omit(data3)

dplyr_data <- data3 %>% group_by(R_STATE) %>% summarise(Trust_Media = round(mean(QB2_B), digits = 2), Trust_Government = round(mean(QB2_A), digits =2), Trust_Police = round(mean(QB2_C),digits =2), Trust_LegalSystem = round(mean(QB2_D),digits =2), Overall_Trust = round((sum(mean(QB2_B) + mean(QB2_A) + mean(QB2_C)+ mean(QB2_D))/4),digits=2))

# Leaflet
spdf <- tigris::states()

data_combine <- spdf@data%>% left_join(dplyr_data, by = c(STUSPS
 = "R_STATE"))
spdf@data <- data_combine

m = leaflet(spdf) %>% 
    setView(lat=37.8, lng=-96 , zoom=4) %>%
    addTiles(group = "OpenStreetMap") %>%
    addProviderTiles(providers$Stamen.Toner, group = "Toner")  %>%
    addPolygons(group = "Trust Media",
      stroke = FALSE, fillOpacity = 0.5, smoothFactor = 0.5,
      color = ~colorNumeric("RdYlGn", Trust_Media)(Trust_Media),
      popup = paste("State:",spdf$STUSPS,"<br/>",
                    "Trust Media:",round(spdf$Trust_Media,2),"<br/>",
                    "Trust Government:",round(spdf$Trust_Government,2),"<br/>",
                    "Trust Police:",round(spdf$Trust_Police,2),"<br/>",
                    "Trust Legal System:",round(spdf$Trust_LegalSystem,2),"<br/>",
                    "Overall Trust Level:",round(spdf$Overall_Trust,2))) %>%
    addPolygons(group = "Tend to Trust Government", data = subset(spdf, Trust_Government>2.7),
                opacity = 1.0, stroke = TRUE, color = "black", weight=2) %>%
    addPolygons(group = "Tend to Trust Police", data = subset(spdf, Trust_Police>2.5),
                opacity = 1.0, stroke = TRUE, color = "red", weight=2) %>%
      addPolygons(group = "Tend to Trust Legal System", data = subset(spdf, Trust_LegalSystem>2.7),
                opacity = 1.0, stroke = TRUE, color = "blue", weight=2) %>%
    addLayersControl(
    baseGroups = c("OpenStreetMap", "Toner"),
    overlayGroups = c("Trust Media","Tend to Trust Government","Tend to Trust Police","Tend to Trust Legal System"),
    options = layersControlOptions(collapsed = TRUE))


m <- m %>% addLegend("bottomright", 
    pal = colorNumeric("RdYlGn", spdf$Trust_Media), values = ~Trust_Media,
    title = "Trust in Media", opacity = 0.5)

m
```


## Middle East Barometer

```{r ME, echo = FALSE, message = FALSE, warning = FALSE}
# Import data
load("32302-0001-Data.rda")
mideast <- da32302.0001

# countries # check the reconding
mideast$countries <- gsub("\\s*\\([^\\)]+\\) ", "", as.character(mideast$MCOUNTRY))
# check for correct coding
# unique(mideast$countries)

press <- ggplot(data = mideast, aes(x = MYEAR, y = as.numeric(M301L))) +
  stat_summary(fun.y = "mean", geom = "line") +
  scale_y_continuous("Trust in the Press", trans = "reverse") +
  scale_x_continuous("Year", breaks = unique(mideast$MYEAR))
tv <- ggplot(data = mideast, aes(x = MYEAR, y = as.numeric(M301H))) +
  stat_summary(fun.y = "mean", geom = "line") +
  scale_y_continuous("Trust in the Press", trans = "reverse") +
  scale_x_continuous("Year", breaks = unique(mideast$MYEAR))

combo <- ggplot(mideast, aes(x = MYEAR)) + 
  scale_x_continuous("Year", breaks = unique(mideast$MYEAR)) +
  stat_summary(aes(y = as.numeric(M301L), col = "blue"), fun.y = "mean", geom = "line") +
  stat_summary(aes(y = as.numeric(M301H), col = "red"), fun.y = "mean", geom = "line") +
  scale_y_continuous("Trust in the Media", trans = "reverse") +
  scale_colour_discrete("Media", labels = c("Press", "TV"))


mideast_ctyr <- mideast %>% group_by(MYEAR, countries) %>%
  summarise(Press = mean(as.numeric(M301L), na.rm = TRUE), 
            TV = mean(as.numeric(M301H), na.rm = TRUE))


mideast_ly <- mideast %>% group_by(MYEAR) %>%
  summarise(Press = mean(as.numeric(M301L), na.rm = TRUE), 
            TV = mean(as.numeric(M301H), na.rm = TRUE))
cntr <- aggregate(countries ~ MYEAR, mideast_ctyr, paste)
mideast_ly <- mideast_ly %>%
  left_join(cntr, by = c("MYEAR" = "MYEAR"))

plot_ly(mideast_ly, x = ~MYEAR, y = ~Press, type = "scatter", mode = "lines+markers", name = "Press") %>%
  add_trace(y = ~TV, name = "TV") %>%
  layout(title = "Yearly Trends in Middle Eastern Trust in Media",
         yaxis = list(autorange = "reversed"),
         xaxis = list(title = "Year")) # text = ~paste('Countries: ', unlist(countries))

mideast_cool <- group_by(mideast, countries) %>%
  summarise(Press_mean = mean(as.numeric(M301L), na.rm = T), 
            TV_mean = mean(as.numeric(M301H), na.rm = T))

if (!require("rworldmap")) {
 install.packages("rworldmap", dependencies = TRUE)
  library(rworldmap)}

mideast_map <- getMap()
mideast_map <- mideast_map[as.character(mideast_map$NAME) %in% mideast$countries, ]

mideast_map@data <- mideast_map@data %>%
  left_join(mideast_cool, by = c("NAME" = "countries"))

if (!require("leaflet")) {
 install.packages("leaflet", dependencies = TRUE)
  library(leaflet)}

leaflet(mideast_map) %>% addTiles() %>%
  addPolygons(fillColor = topo.colors(17, alpha = NULL), stroke = FALSE,
              fillOpacity = 0.5, smoothFactor = 0.5, 
              color = ~colorQuantile("RdYlGn", Press_mean)(Press_mean),
              popup = paste("Country:", mideast_map$NAME,"<br/>",
                  "Trust in Press:", round(mideast_map$Press_mean, 2),"<br/>",
                  "Trust in TV:", round(mideast_map$TV_mean, 2)))
```



